This is the Title

### 2017-03-07 abc/paper/paper.tex
Put relocations after CS, so that it's not corrupting code, and do so using a printable word. Some debugging code and simple seg:off solver

>>>>

interesting bugs:
  DI <- [DI]

write about load16 tmp <- tmp; it's amazing now.
(benchmark history shows performance gains..)

words contained in this paper

style points for:
- put relocations a little later after CS, so that we can mark
  with text the spot where they go.

opportunity for style points, like making your phone number into
a word:

 j ? X 4 ?   (4 can alternatively be $ or ,)

 NEED TO FIX:
  - jump at least 0x20
  - store16 (not printable)
  - Not bug
  - some kind of output other than \_putc

dosbox patches, wing commander

ascii art in paper
